atlantisom: simulated ecosystem datasets for assessment model performance testing

### 2020-06-10 atlantisom_landingpage.Rmd
add detailed data flow section

@@

## External Resources

>>>>

## Detailed data flow

Have these Atlantis input files in a directory:

- The .bgm file defining model geometry
- The initial conditions/biomass pools .nc 
- The functional groups .csv
- The fishery groups .csv
- The biology .prm
- The run prm (.xml version)

At present,`atlantisom` uses the following Atlantis output files, where [...] is a model-specific prefix. They should be in the same directory as the input files above:

- [...]BiomIndx.txt
- [...]Catch.txt
- [...]CatchPerFishery.txt
- [...]DietCheck.txt
- [...]YOY.txt
- [...].nc
- [...]CATCH.nc
- [...]PROD.nc
- [...]ANNAGEBIO.nc (if available)
- [...]ANNAGECATCH.nc (if available)

Get the truth:
![](docs/images/atlantisomDataFlow_truth-link.png)

Generate the data:
![](docs/images/atlantisomDataFlow_data.png)

@@

## More information
